Carbon Nucleosynthesis

### 2023-04-08 thesis/tex/main.tex
thesis ?

\titleformat{\chapter}{\normalfont\normalsize\centering}{Chapter \thechapter:}{1em}{}
\titleformat{\section}{\normalfont\normalsize\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\centering}{\thesubsection}{1em}{}
% \titlespacing*{\chapter}{0pt}{0pt}{40pt} 
% \titlespacing*{\section}{0pt}{0pt}{20pt}
\renewcommand{\contentsname}{Table of Contents}
\AtBeginDocument{
      \renewcommand{\bibsection}{\chapter*{\bibname}}
  }

@@

\begin{titlepage}
   \begin{center}
       \vfill
       \textbf{The Galactic Chemical Evolution of Carbon} \\
       [3\baselineskip]
        Undergraduate Research Thesis\\
       [3\baselineskip]
    Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University \\
       [3\baselineskip]
        by \\
       {Daniel Alexander Boyea}\\
       [3\baselineskip]
       The Ohio State University\\
       April 2023\\
       [3\baselineskip]
       Project Advisor: David Weinberg, Department of Astronomy
       % Rolando Vald\'es Aguilar\\
       \vfill
   \end{center}
\end{titlepage}

@@

Galactic chemical evolution (GCE) aims to understand the chemical and star formation history of galaxies. At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy). Different chemical elements are produced in different sites, so stars leave traces of the Galaxy's chemical history. Through \textit{Galactic Archeology}, I can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.

>>>>

\titleformat{\chapter}{\normalfont\normalsize\centering}{\thechapter.}{1em}{}
\titleformat{\section}{\normalfont\normalsize\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\centering}{\thesubsection}{1em}{}
% \titlespacing*{\chapter}{0pt}{0pt}{40pt} 
% \titlespacing*{\section}{0pt}{0pt}{20pt}
\renewcommand{\contentsname}{Table of Contents}
\AtBeginDocument{
      \renewcommand{\bibsection}{\chapter*{\bibname}}
  }

@@

\begin{titlepage}
   \begin{center}
       \vspace*{5\baselineskip}
       \textbf{The Galactic Chemical Evolution of Carbon} \\
       \vspace*{3\baselineskip}
        Undergraduate Research Thesis\\
       \vspace*{3\baselineskip}
    Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University \\
       \vspace*{3\baselineskip}
        by \\
       \vspace*{3\baselineskip}
       {Daniel Alexander Boyea}\\
       \vspace*{3\baselineskip}
       The Ohio State University\\
       April 2023\\
       \vspace*{3\baselineskip}
       Project Advisor: David Weinberg, Department of Astronomy
       % Rolando Vald\'es Aguilar\\
       \vfill
   \end{center}
\end{titlepage}

@@

Galactic chemical evolution (GCE) aims to understand the chemical and star formation history of galaxies. At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy). Different chemical elements are produced in different sites, so stars leave traces of the Galaxy's chemical history. Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.
